Smart Model Elimination for Efficient Automated Machine Learning

### 2024-06-22 paper/paper.tex
remove "

Machine learning (ML) is a type of artificial intelligence (AI) that uses a variety of algorithms to interpret data and extrapolate from it, making predictions based on observed trends. Individual models are trained on datasets to become smarter so as to make predictions based on new data. The development and optimization of these models is a time-consuming process involving statistical nuances and complex learning strategies. This has led to the emergence of Automated Machine Learning (AutoML) frameworks and research.

One sector of the global industry that has the most potential for beneficial integration of AutoML frameworks is healthcare, particularly in developing countries. These countries have severe shortages of healthcare workers and limited tools for diagnosis. For example, Africa has 2.3 healthcare workers per 1000 individuals, while the Americas have 24.8 healthcare workers per 1000. The World Health Organization (WHO) emphasized that this deficit is growing every year and will likely reach 18 million personnel by 2030. The use of AI in healthcare has been varied. Medical AI's typically automate repetitive tasks, making time consumption a primary concern. This coupled with a lack of adequate resources makes designing faster diagnostic systems for developing countries' medical sectors a pivotal issue. 
%
Most AutoML frameworks implement some form of model selection where a pool of models are filtered until a final model is selected. However, these frameworks require that every model to be run to filter out. In theory, this means that much energy is spent training models that are unlikely to be selected. We propose SMEML, a novel model selection algorithm that automatically eliminates models that it believes will not be performant.

@@

\begin{table}
  \caption{Survey of Existing AutoML Frameworks}
  \label{automl-survey}
  \centering
  \begin{tabular}{lllllllll}
    \toprule
    Framework & EOU & M & FE & TM & HPT & Inter & Custom\\
    \midrule
    H2O AutoML & Easy & 6 & Basic & Yes & Auto & SHAP & High\\
    TPOT & Hard & 10 & Basic & No & Genetic & POJO & Moderate\\
    MLJAR & Easy & 12 & Advanced & Yes & Auto & Basic & High\\
    FLAML & Easy & 9 & Limited & Yes & Auto & SHAP & Low-Moderate\\
    LightAutoML & Easy & 11 & Advanced & Yes & Auto & Basic & Moderate\\
    \bottomrule
  \end{tabular}
  \captionsetup{font=footnotesize}
  \caption*{\textbf{Abbreviations}: EOU: Ease of Use, M: \# of models evaluated by framework, FE: Feature Engineering, TM: Time Management, HPT: Hyper-Parameter Tuning, Inter: Interface, Custom: Customization}
\end{table}
We systematically reviewed and compared six different AutoML frameworks, comparing every feature relevant to medical implementation. Of these six, we wanted to take a closer look at four: FLAML, H2O, MLJAR, and TPOT.

Taking a closer look at four AutoML standards, we can observe pros and cons in their theoretical application to medicine and research. FLAML uses blend search hyper-parameter optimization and focuses on lightweight models, making it quick and applicable to repetitive tasks in the medical sphere. It supports imputation techniques for missing values with user specification and has an intuitive API, making it moderately user-friendly for minimally trained healthcare workers. H2O has a wider variety of supported algorithms that may or may not be appropriate for medical diagnosis, making it slower than FLAML on Mean. In one trial, more than half of FLAML's performances in one minute were better than or equal to H20's performances in one hour. H2O has automatic and multi-faceted methods of dealing with missing values and flexible interfaces in R and Python, making it intuitive for users. MLJAR uses more advanced algorithms such as light gradient boosting and neural networks. It automatically deals with missing values and is known for its automated user interface. TPOT uses genetic programming. It builds pipelines over multiple generations, which can be time consuming. It has built-in pre-processing for missing values, but the genetic programming can require fine-tuning from users.

@@

\section{Methodology}
When considering a specific dataset, various aspects regarding the distribution and relationship within the data can give us clues as to which models are likely to perform best. For example, linear models tend to work better on datasets where there is a linear relationship between features. As a result, we can develop a boosting model to predict the best models based off extracted attributes from a dataset. These extracted attributes are shown in Table 2.

@@

\section*{References}

\medskip
{
\small

% references here

\end{document}

>>>>

Machine learning (ML) is a type of artificial intelligence (AI) that uses a variety of algorithms to interpret data and extrapolate from it, making predictions based on observed trends. Individual models are trained on datasets to become smarter so as to make predictions based on new data. The development and optimization of these models is a time-consuming process involving statistical nuances and complex learning strategies. This has led to the emergence of Automated Machine Learning (AutoML) frameworks and research [1].

One sector of the global industry that has the most potential for beneficial integration of AutoML frameworks is healthcare, particularly in developing countries. These countries have severe shortages of healthcare workers and limited tools for diagnosis. For example, Africa has 2.3 healthcare workers per 1000 individuals, while the Americas have 24.8 healthcare workers per 1000 [2]. The World Health Organization (WHO) emphasized that this deficit is growing every year and will likely reach 18 million personnel by 2030 [3]. The use of AI in healthcare has been varied. Medical AI's typically automate repetitive tasks, making time consumption a primary concern [4]. This coupled with a lack of adequate resources makes designing faster diagnostic systems for developing countries' medical sectors a pivotal issue. 
%
Most AutoML frameworks implement some form of model selection where a pool of models are filtered until a final model is selected. However, these frameworks require that every model to be run to filter out [1]. In theory, this means that much energy is spent training models that are unlikely to be selected. We propose SMEML, a novel model selection algorithm that automatically eliminates models that it believes will not be performant.

@@

\begin{table}
  \caption{Survey of Existing AutoML Frameworks}
  \label{automl-survey}
  \centering
  \begin{tabular}{lllllllll}
    \toprule
    Framework & EOU & M & FE & TM & HPT & Inter & Custom\\
    \midrule
    H2O AutoML & Easy & 6 & Basic & Yes & Auto & SHAP & High\\
    TPOT & Hard & 10 & Basic & No & Genetic & POJO & Moderate\\
    MLJAR & Easy & 12 & Advanced & Yes & Auto & Basic & High\\
    FLAML & Easy & 9 & Limited & Yes & Auto & SHAP & Low-Moderate\\
    LightAutoML & Easy & 11 & Advanced & Yes & Auto & Basic & Moderate\\
    \bottomrule
  \end{tabular}
  \captionsetup{font=footnotesize}
  \caption*{\textbf{Abbreviations}: EOU: Ease of Use, M: \# of models evaluated by framework, FE: Feature Engineering, TM: Time Management, HPT: Hyper-Parameter Tuning, Inter: Interface, Custom: Customization}
\end{table}
We systematically reviewed and compared five different AutoML frameworks, comparing every feature relevant to medical implementation [5, 6, 7, 8, 9, 10, 11, 12, 13]. Of these six, we wanted to take a closer look at four: FLAML, H2O, MLJAR, and TPOT.

Taking a closer look at four AutoML standards, we can observe pros and cons in their theoretical application to medicine and research. FLAML uses blend search hyper-parameter optimization and focuses on lightweight models, making it quick and applicable to repetitive tasks in the medical sphere. It supports imputation techniques for missing values with user specification and has an intuitive API, making it moderately user-friendly for minimally trained healthcare workers [11, 12]. H2O has a wider variety of supported algorithms that may or may not be appropriate for medical diagnosis, making it slower than FLAML on average. In one trial, more than half of FLAML's performances in one minute were better than or equal to H20's performances in one hour [12]. H2O has automatic and multi-faceted methods of dealing with missing values and flexible interfaces in R and Python, making it intuitive for users [5, 6]. MLJAR uses more advanced algorithms such as light gradient boosting and neural networks. It automatically deals with missing values and is known for its automated user interface [9, 10]. TPOT uses genetic programming. It builds pipelines over multiple generations, which can be time consuming. It has built-in pre-processing for missing values, but the genetic programming can require fine-tuning from users [7, 8].

@@

\section{Methodology}
When considering a specific dataset, various aspects regarding the distribution and relationship within the data can give us clues as to which models are likely to perform best. For example, linear models tend to work better on datasets where there is a linear relationship between features [14]. As a result, we can develop a boosting model to predict the best models based off extracted attributes from a dataset. These extracted attributes are shown in Table 2.

@@

\section*{References}
\medskip
{
\small

[1] He, Xin, et al. “AutoML: A Survey of the State-of-the-Art.” Knowledge-Based Systems, journal-article, 16 Apr. 2021, arxiv.org/pdf/1908.00709.
[2] Nchasi, Goodluck, et al. “Challenges Faced by African Healthcare Workers During the Third Wave of the Pandemic.” Health Science Reports, vol. 5, no. 6, Oct. 2022, doi:10.1002/hsr2.893.
[3] Global Strategy on Human Resources for Health: Workforce 2030. World Health Organization, 2016, iris.who.int/bitstream/handle/10665/250368/9789241511131-eng.pdf?sequence=1.
[4] Bajwa, Junaid, et al. “Artificial Intelligence in Healthcare: Transforming the Practice of Medicine.” Future Healthcare Journal, vol. 8, no. 2, July 2021, pp. e188–94, doi:10.7861/fhj.2021-0095.
[5] LeDell, E., and S. Poirier. “H2O AutoML: Scalable Automatic Machine Learning.” 7th ICML Workshop on Automated Machine Learning, 2020, \url{www.automl.org/wp-content/uploads/2020/07/AutoML_2020_paper_61.pdf}.
[6] “H2oai/H2o-3: H2O Is an Open Source, Distributed, Fast and Scalable Machine Learning Platform: Deep Learning, Gradient Boosting (GBM) \& XGBoost, Random Forest, Generalized Linear Modeling (GLM With Elastic Net), K-Means, PCA, Generalized Additive Models (GAM), RuleFit, Support Vector Machine (SVM), Stacked Ensembles, Automatic Machine Learning (AutoML), Etc.” GitHub, github.com/h2oai/h2o-3.
[7] Olson, Randal S., 1, et al. Automating Biomedical Data Science Through Tree-based Pipeline Optimization. journal-article, 28 Jan. 2016, arxiv.org/pdf/1601.07925.
[8] “EpistasisLab/Tpot: A Python Automated Machine Learning Tool That Optimizes Machine Learning Pipelines Using Genetic Programming.” GitHub, github.com/EpistasisLab/tpot.
[9] “Mljar/Mljar-supervised: Python Package for AutoML on Tabular Data With Feature Engineering, Hyper-Parameters Tuning, Explanations and Automatic Documentation.” GitHub, github.com/mljar/mljar-supervised.
[10] Conrad, Felix, et al. “Benchmarking AutoML for Regression Tasks on Small Tabular Data in Materials Design.” Scientific Reports, vol. 12, no. 1, Nov. 2022, doi:10.1038/s41598-022-23327-1.
[11] Shang, Zhi, et al. "FLAML: A Fast and Lightweight AutoML Library." arXiv, 11 Nov. 2019, arxiv.org/pdf/1911.04706.
[12] "FLAML: A Fast Library for AutoML and Tuning." GitHub, github.com/microsoft/FLAML.
[13] “Sb-ai-lab/LightAutoML: Fast and Customizable Framework for Automatic ML Model Creation (AutoML).” GitHub, github.com/sb-ai-lab/LightAutoML.
[14] Akalin, Altuna. 3.3 Relationship Between Variables: Linear Models and Correlation | Computational Genomics With R. 30 Sept. 2020, compgenomr.github.io/book/relationship-between-variables-linear-models-and-correlation.html.
\end{document}
